---
title: "GTAA Performance Report"
author: "Xuran ZENG"
date: "2020/11/25"
output: 
  html_document: 
    toc: yes
    toc_float: true  
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE}
library(xts)
library(PerformanceAnalytics)
library(lubridate)
library(quantmod)



source("C:/Users/carol/Desktop/asset_allocation/cal_ret.R")


```

```{r echo=FALSE}
weights_data.raw3<-read.csv("C:\\Users\\carol\\Desktop\\asset_allocation\\GTAA\\assets_weights3.csv") ## read in weights data 
weights_data3<-xts(weights_data.raw3[,-1],ymd(weights_data.raw3[,1])) ## convert to xts

weights_data.raw6<-read.csv("C:\\Users\\carol\\Desktop\\asset_allocation\\GTAA\\assets_weights6.csv") ## read in weights data 
weights_data6<-xts(weights_data.raw6[,-1],ymd(weights_data.raw6[,1])) ## convert to xts

returns_data.raw<-read.csv("C:\\Users\\carol\\Desktop\\asset_allocation\\GTAA\\assets_returns.csv") ## read in returns data 
returns_data<-xts(returns_data.raw[,-1],ymd(returns_data.raw[,1])) ## convert to xts
```

# Strategy introduction
## Setting

##### Horizon: 2008-01-01/2020-07-14
##### Assets:IWD	MTUM	IWN	IWM	EFA	EEM	IEF	BWX	LQD	TLT	DBC	GLD	VNQ
##### Benchmark: 60/40 benchmark with SPY and TLT


## Process
##### downloaded data from yahoo Finance.

#### Generate SPY, benchmark and portfolio returns
##### generate 60/40 benchmark with SPY and TLT (“benchmark”)
```{r}
benchmark.ret<-cbind(returns_data$SPY, returns_data$TLT)
benchmark.portf<-portf.sixty_fourty(benchmark.ret, rebalance_on="months", verbose=T)
```

```{r echo=FALSE}
bench.ret<-benchmark.portf$returns
colnames(bench.ret)<-"Benchmark"

SPY.ret<-returns_data$SPY
colnames(SPY.ret)<-"SPY"
```

##### generate GTAA3 & GTAA6 portfolio 
```{r}
portf3 <- Return.portfolio(returns_data, weights = weights_data3, verbose=T)
portf6 <- Return.portfolio(returns_data, weights = weights_data6, verbose=T)

portf.ret3<-portf3$returns
colnames(portf.ret3)<-"GTAA3"

portf.ret6<-portf6$returns
colnames(portf.ret6)<-"GTAA6"


```

# Strategy Performance

## Data from 2015-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret3['2015-01-01/2020-01-01'],portf.ret6['2015-01-01/2020-01-01'], bench.ret['2015-01-01/2020-01-01'],SPY.ret['2015-01-01/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret3['2015-01-01/2020-01-01'],portf.ret6['2015-01-01/2020-01-01'], bench.ret['2015-01-01/2020-01-01'],SPY.ret['2015-01-01/2020-01-01'])
colnames(ret)<-c("GTAA3","GTAA6","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret3['2015-01-01/2020-01-01'],portf.ret6['2015-01-01/2020-01-01'], bench.ret['2015-01-01/2020-01-01'],SPY.ret['2015-01-01/2020-01-01']),
                                   c("GTAA3","GTAA6","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf3$BOP.Value['2015-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(portf6$BOP.Value['2015-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
```


## Data from 2017-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret3['2017-01-01/2020-01-01'],portf.ret6['2017-01-01/2020-01-01'], bench.ret['2017-01-01/2020-01-01'],SPY.ret['2017-01-01/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret3['2017-01-01/2020-01-01'],portf.ret6['2017-01-01/2020-01-01'], bench.ret['2017-01-01/2020-01-01'],SPY.ret['2017-01-01/2020-01-01'])
colnames(ret)<-c("GTAA3","GTAA6","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret3['2017-01-01/2020-01-01'],portf.ret6['2017-01-01/2020-01-01'], bench.ret['2017-01-01/2020-01-01'],SPY.ret['2017-01-01/2020-01-01']),
                                   c("GTAA3","GTAA6","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf3$BOP.Value['2017-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(portf6$BOP.Value['2017-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
```


## Data from 2019-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret3['2019-01-01/2020-01-01'],portf.ret6['2019-01-01/2020-01-01'], bench.ret['2019-01-01/2020-01-01'],SPY.ret['2019-01-01/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret3['2019-01-01/2020-01-01'],portf.ret6['2019-01-01/2020-01-01'], bench.ret['2019-01-01/2020-01-01'],SPY.ret['2019-01-01/2020-01-01'])
colnames(ret)<-c("GTAA3","GTAA6","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret3['2019-01-01/2020-01-01'],portf.ret6['2019-01-01/2020-01-01'], bench.ret['2019-01-01/2020-01-01'],SPY.ret['2019-01-01/2020-01-01']),
                                   c("GTAA3","GTAA6","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf3$BOP.Value['2019-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(portf6$BOP.Value['2019-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
```

## Data from 2019-06-30 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret3['2019-06-30/2020-01-01'],portf.ret6['2019-06-30/2020-01-01'], bench.ret['2019-06-30/2020-01-01'],SPY.ret['2019-06-30/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret3['2019-06-30/2020-01-01'],portf.ret6['2019-06-30/2020-01-01'], bench.ret['2019-06-30/2020-01-01'],SPY.ret['2019-06-30/2020-01-01'])
colnames(ret)<-c("GTAA3","GTAA6","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret3['2019-06-30/2020-01-01'],portf.ret6['2019-06-30/2020-01-01'], bench.ret['2019-06-30/2020-01-01'],SPY.ret['2019-06-30/2020-01-01']),
                                   c("GTAA3","GTAA6","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf3$BOP.Value['2019-06-30/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(portf6$BOP.Value['2019-06-30/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
```

## Year to Date
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret3['2020-01-01/2020-07-14'],portf.ret6['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret3['2020-01-01/2020-07-14'],portf.ret6['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14'])
colnames(ret)<-c("GTAA3","GTAA6","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret3['2020-01-01/2020-07-14'],portf.ret6['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14']),
                                   c("GTAA3","GTAA6","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf3$BOP.Value['2020-01-01/2020-07-14'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(portf6$BOP.Value['2020-01-01/2020-07-14'], date.format="%y/%m", colorset=rainbow12equal, border=NA)
```