
---
title: "HRP Performance Report"
author: "Xuran ZENG"
date: "2020/12/17"
output: 
  html_document: 
    toc: yes
    toc_float: true 
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE}
library(xts)
library(PerformanceAnalytics)
library(lubridate)
library(quantmod)
library(TTR)

source("C:/Users/carol/Desktop/asset_allocation/cal_ret.R")
source("C:/Users/carol/Desktop/asset_allocation/models.R")
```

```{r results="hide"}
library(WindR)
w.start()
begintime<-"2013-07-29"  
endtime<-Sys.time()

symbols<-c("H00909.CSI",  #沪深300材料
         "H00910.CSI",  #沪深300工业
         "H00911.CSI",  #沪深300可选
         "H00912.CSI",  #沪深300消费
         "H00913.CSI",  #沪深300医药
         "H00914.CSI",  #沪深300金融
         "H00915.CSI",  #沪深300信息
         "H00300.CSI",  #沪深300
         "H00905.CSI",  #中证500
         "399606.SZ",   #创业板
         "H00140.SH",   #国债指数
         "518800.SH"   #黄金ETF
         )   
wdata<-as.data.frame(w.wsd(symbols,'close',begintime,endtime))

```

```{r echo=FALSE}
rownames(wdata)<-as.Date(wdata[,'Data.DATETIME'])

wdata<-subset(wdata,select=-c(ErrorCode,Field,Data.DATETIME))

colnames(wdata)<-symbols
```

```{r echo=FALSE}
returns_data<-na.omit(ROC(wdata)) 
bench_data<-returns_data$H00140.SH
returns_data<-subset(returns_data,select=-c(H00140.SH))
```

```{r echo=FALSE}
colnames(returns_data)<-c("材料","工业","可选","消费","医药","金融","信息","沪深300","中证500","创业板","黄金")
returns_data<-as.xts(returns_data)
```

```{r echo=FALSE}
weights_data<-read.csv("C:/Users/carol/Desktop/asset_allocation/HRP/weights.csv") ## read in weights data 
weights_data<-as.numeric(weights_data)



```

```{r echo=FALSE}

benchmark.ret<-cbind(returns_data$沪深300, bench_data)
benchmark.portf<-portf.sixty_fourty(benchmark.ret, rebalance_on="months", verbose=T)

bench.ret<-benchmark.portf$returns
colnames(bench.ret)<-"Benchmark"

equal_weights<-rep(1/ncol(returns_data),ncol(returns_data)) 
equal.ret<-Return.portfolio(returns_data,weights = equal_weights,rebalance_on = "months")
colnames(equal.ret)<-"equal"

portf <- Return.portfolio(returns_data,weights_data, rebalance_on="months", verbose=T)
portf.ret<-portf$returns
colnames(portf.ret)<-"Strategy"
```

```{r echo=FALSE}
ret<-cbind(portf.ret, bench.ret, equal.ret)

colnames<-c("Strategy","Benchmark", "Equal")
```


## Data from 2013-07-31 to today (full sample)
```{r echo=FALSE}
date1 <- '2013-07-31'
date2 <- Sys.Date()
full_sample<-paste(date1,date2,sep = "/")


ret.full_sample<-ret[full_sample,]

```


### Performance Summary
```{r echo=FALSE}
tab.perf(ret.full_sample)
```

```{r echo=FALSE}
charts.PerformanceSummary(ret.full_sample, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(ret.full_sample, colnames)
cal_annual_ret
#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value[full_sample], date.format="%y/%m", colorset=rainbow12equal, border=NA)
```

## Data from 2015-01-01 to 2020-01-01
```{r echo=FALSE}

five_years<-'2015-01-01/2020-01-01'

ret.five_years<-ret[five_years,]

```

### Performance Summary
```{r echo=FALSE}
tab.perf(ret.five_years)
```

```{r echo=FALSE}
charts.PerformanceSummary(ret.five_years, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(ret.five_years, colnames)
cal_annual_ret
#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value[five_years], date.format="%y/%m", colorset=rainbow12equal, border=NA)
```

## Data from 2017-01-01 to 2020-01-01
```{r echo=FALSE}

three_years<-'2017-01-01/2020-01-01'

ret.three_years<-ret[three_years,]

```

### Performance Summary
```{r echo=FALSE}
tab.perf(ret.three_years)
```

```{r echo=FALSE}
charts.PerformanceSummary(ret.three_years, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(ret.three_years, colnames)
cal_annual_ret
#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value[three_years], date.format="%y/%m", colorset=rainbow12equal, border=NA)
```



## Data from 2019-01-01 to 2020-01-01
```{r echo=FALSE}

one_year<-'2019-01-01/2020-01-01'

ret.one_year<-ret[one_year,]

```

### Performance Summary
```{r echo=FALSE}
tab.perf(ret.one_year)
```

```{r echo=FALSE}
charts.PerformanceSummary(ret.one_year, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(ret.one_year, colnames)
cal_annual_ret
#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value[one_year], date.format="%y/%m", colorset=rainbow12equal, border=NA)
```


## Data from 2019-06-30 to 2020-01-01
```{r echo=FALSE}

six_months<-'2019-06-30/2020-01-01'

ret.six_months<-ret[six_months,]

```

### Performance Summary
```{r echo=FALSE}
tab.perf(ret.six_months)
```

```{r echo=FALSE}
charts.PerformanceSummary(ret.six_months, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(ret.six_months, colnames)
cal_annual_ret
#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value[six_months], date.format="%y/%m", colorset=rainbow12equal, border=NA)
```

## Year to Date
```{r echo=FALSE}
date1 <- '2020-01-01'
date2 <- Sys.Date()
ytd<-paste(date1,date2,sep = "/")

ret.ytd<-ret[ytd,]
```

### Performance Summary
```{r echo=FALSE}
tab.perf(ret.ytd)
```

```{r echo=FALSE}
charts.PerformanceSummary(ret.ytd, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(ret.ytd, colnames)
cal_annual_ret
#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value[ytd], date.format="%y/%m", colorset=rainbow12equal, border=NA)
```
