---
title: "RAA Performance  Report"
author: "Xuran ZENG"
date: "2020/10/30"
output: 
  html_document: 
    toc: yes
    toc_float: true  

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE}
library(xts)
library(PerformanceAnalytics)
library(lubridate)
library(quantmod)

setwd("C:/Users/carol/Desktop/asset_allocation")
source("cal_ret.R")

portf.sixty_fourty<-function(ret,...){
  ret1<-ret[,1]
  ret2<-ret[,2]
  weights<-c(0.6, 0.4)
  Return.portfolio(ret,weights,...)
}

RAA.Balanced <- function(ret,...){
  ret1<-ret[,1]
  ret2<-ret[,2]
  ret2<-ret[,3]
  weights<-c(0.4, 0.4, 0.2)
  Return.portfolio(ret,weights,...)
}

RAA.Aggressive <- function(ret,...){
  ret1<-ret[,1]
  ret2<-ret[,2]
  ret2<-ret[,3]
  weights<-c(0.8, 0.1, 0.1)
  Return.portfolio(ret,weights,...)
}

```

```{r echo=FALSE}
returns_data.raw<-read.csv("C:\\Users\\carol\\Desktop\\asset_allocation\\all_assets.csv") ## read in price data 
returns_data<-xts(returns_data.raw[,-1],ymd(returns_data.raw[,1])) ## convert to xts

```

# Strategy introduction
## Setting
##### Principle: Buy and Hold
##### RAA Balanced: 40% Equities+40% Real Assets+20% Bond
##### RAA Aggressive: 80% Equities+10% Real Assets+10% Bond
##### Horizon: 2008-01-01/2020-07-14
##### Assets: SPY,VNQ, IEF
##### Benchmark: 60/40 benchmark with SPY and TLT

Source: [Robust Asset Allocation](https://alphaarchitect.com/2014/12/02/the-robust-asset-allocation-raa-index/)

## Process
##### downloaded data from yahoo Finance.

#### Generate SPY, benchmark and portfolio returns
##### generate 60/40 benchmark with SPY and TLT (“benchmark”)
```{r}
benchmark.ret<-cbind(returns_data$SPY, returns_data$TLT)
benchmark.portf<-portf.sixty_fourty(benchmark.ret, rebalance_on="months", verbose=T)
```

```{r echo=FALSE}
bench.ret<-benchmark.portf$returns
colnames(bench.ret)<-"Benchmark"

SPY.ret<-returns_data$SPY
colnames(SPY.ret)<-"SPY"
```

##### generate RAA.Balanced & RAA.Aggressive portfolio 
```{r}
RAA.Balanced.ret<-cbind(returns_data$SPY, returns_data$VNQ, returns_data$IEF)
RAA.Balanced.portf<-RAA.Balanced(RAA.Balanced.ret, rebalance_on="months", verbose=T)

RAA.Aggressive.ret<-cbind(returns_data$SPY, returns_data$VNQ, returns_data$IEF)
RAA.Aggressive.portf<-RAA.Aggressive(RAA.Aggressive.ret, rebalance_on="months", verbose=T)

Balanced.ret<-RAA.Balanced.portf$returns
colnames(Balanced.ret)<-"RAA.Balanced"

Aggressive.ret<-RAA.Aggressive.portf$returns
colnames(Aggressive.ret)<-"RAA.Aggressive"
```

# Strategy Performance

## Data from 2015-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(Balanced.ret['2015-01-01/2020-01-01'],Aggressive.ret['2015-01-01/2020-01-01'], bench.ret['2015-01-01/2020-01-01'],SPY.ret['2015-01-01/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(Balanced.ret['2015-01-01/2020-01-01'],Aggressive.ret['2015-01-01/2020-01-01'], bench.ret['2015-01-01/2020-01-01'],SPY.ret['2015-01-01/2020-01-01'])
colnames(ret)<-c("RAA.Balanced","RAA.Aggressive","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(Balanced.ret['2015-01-01/2020-01-01'],Aggressive.ret['2015-01-01/2020-01-01'], bench.ret['2015-01-01/2020-01-01'],SPY.ret['2015-01-01/2020-01-01']),
                                   c("RAA.Balanced","RAA.Aggressive","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(RAA.Balanced.portf$BOP.Value['2015-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(RAA.Aggressive.portf$BOP.Value['2015-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
```


## Data from 2017-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(Balanced.ret['2017-01-01/2020-01-01'],Aggressive.ret['2017-01-01/2020-01-01'], bench.ret['2017-01-01/2020-01-01'],SPY.ret['2017-01-01/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(Balanced.ret['2017-01-01/2020-01-01'],Aggressive.ret['2017-01-01/2020-01-01'], bench.ret['2017-01-01/2020-01-01'],SPY.ret['2017-01-01/2020-01-01'])
colnames(ret)<-c("RAA.Balanced","RAA.Aggressive","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(Balanced.ret['2017-01-01/2020-01-01'],Aggressive.ret['2017-01-01/2020-01-01'], bench.ret['2017-01-01/2020-01-01'],SPY.ret['2017-01-01/2020-01-01']),
                                   c("RAA.Balanced","RAA.Aggressive","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(RAA.Balanced.portf$BOP.Value['2017-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(RAA.Aggressive.portf$BOP.Value['2017-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
```


## Data from 2019-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(Balanced.ret['2019-01-01/2020-01-01'],Aggressive.ret['2019-01-01/2020-01-01'], bench.ret['2019-01-01/2020-01-01'],SPY.ret['2019-01-01/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(Balanced.ret['2019-01-01/2020-01-01'],Aggressive.ret['2019-01-01/2020-01-01'], bench.ret['2019-01-01/2020-01-01'],SPY.ret['2019-01-01/2020-01-01'])
colnames(ret)<-c("RAA.Balanced","RAA.Aggressive","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(Balanced.ret['2019-01-01/2020-01-01'],Aggressive.ret['2019-01-01/2020-01-01'], bench.ret['2019-01-01/2020-01-01'],SPY.ret['2019-01-01/2020-01-01']),
                                   c("RAA.Balanced","RAA.Aggressive","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(RAA.Balanced.portf$BOP.Value['2019-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(RAA.Aggressive.portf$BOP.Value['2019-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
```

## Data from 2019-06-30 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(Balanced.ret['2019-06-30/2020-01-01'],Aggressive.ret['2019-06-30/2020-01-01'], bench.ret['2019-06-30/2020-01-01'],SPY.ret['2019-06-30/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(Balanced.ret['2019-06-30/2020-01-01'],Aggressive.ret['2019-06-30/2020-01-01'], bench.ret['2019-06-30/2020-01-01'],SPY.ret['2019-06-30/2020-01-01'])
colnames(ret)<-c("RAA.Balanced","RAA.Aggressive","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(Balanced.ret['2019-06-30/2020-01-01'],Aggressive.ret['2019-06-30/2020-01-01'], bench.ret['2019-06-30/2020-01-01'],SPY.ret['2019-06-30/2020-01-01']),
                                   c("RAA.Balanced","RAA.Aggressive","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(RAA.Balanced.portf$BOP.Value['2019-06-30/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(RAA.Aggressive.portf$BOP.Value['2019-06-30/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
```

## Year to Date
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(Balanced.ret['2020-01-01/2020-07-14'],Aggressive.ret['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14']))
```

```{r echo=FALSE}
ret<-cbind(Balanced.ret['2020-01-01/2020-07-14'],Aggressive.ret['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14'])
colnames(ret)<-c("RAA.Balanced","RAA.Aggressive","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(Balanced.ret['2020-01-01/2020-07-14'],Aggressive.ret['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14']),
                                   c("RAA.Balanced","RAA.Aggressive","bench","SPY"))
cal_annual_ret

```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(RAA.Balanced.portf$BOP.Value['2020-01-01/2020-07-14'], date.format="%y/%m", colorset=rainbow12equal, border=NA) 
chart.StackedBar(RAA.Aggressive.portf$BOP.Value['2020-01-01/2020-07-14'], date.format="%y/%m", colorset=rainbow12equal, border=NA)
```