---
title: "TDM Performance Report"
author: "Xuran ZENG"
date: "2020/11/27"
output: 
  html_document: 
    toc: yes
    toc_float: true 
---



```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

```{r echo=FALSE}
library(xts)
library(PerformanceAnalytics)
library(lubridate)
library(quantmod)



source("C:/Users/carol/Desktop/asset_allocation/cal_ret.R")

```

# Strategy introduction
## Setting
##### Horizon: 2008-01-01/2020-07-14
##### assets: SPY, VEU, BND
##### comparison assets: BIL
##### Benchmark: 60/40 benchmark with SPY and BND



## Process
##### downloaded data from yahoo Finance.
```{r echo=FALSE}
weights_data.raw<-read.csv("C:\\Users\\carol\\Desktop\\asset_allocation\\TDM\\assets_weights.csv") ## read in weights data 
weights_data<-xts(weights_data.raw[,-1],ymd(weights_data.raw[,1])) ## convert to xts

returns_data.raw<-read.csv("C:\\Users\\carol\\Desktop\\asset_allocation\\TDM\\assets_returns.csv") ## read in returns data 
returns_data<-xts(returns_data.raw[,-1],ymd(returns_data.raw[,1])) ## convert to xts


```


#### Generate SPY, benchmark and portfolio returns
##### generate 60/40 benchmark with SPY and TLT (“benchmark”)
```{r}
benchmark.ret<-cbind(returns_data$SPY, returns_data$BND)
benchmark.portf<-portf.sixty_fourty(benchmark.ret, rebalance_on="months", verbose=T)
```

```{r echo=FALSE}
bench.ret<-benchmark.portf$returns
colnames(bench.ret)<-"Benchmark"

SPY.ret<-returns_data$SPY
colnames(SPY.ret)<-"SPY"
```

##### generate TDM portfolio 
```{r}
portf <- Return.portfolio(returns_data, weights = weights_data, verbose=T)
```

```{r echo=FALSE}
portf.ret<-portf$returns
colnames(portf.ret)<-"Strategy"
```

# Strategy Performance
## Data from 2008-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret['2008-01-01/2020-01-01'], bench.ret['2008-01-01/2020-01-01'],SPY.ret['2008-01-01/2020-01-01']))

```

```{r echo=FALSE}
ret<-cbind(portf.ret['2008-01-01/2020-01-01'], bench.ret['2008-01-01/2020-01-01'],SPY.ret['2008-01-01/2020-01-01'])
colnames(ret)<-c("TDM","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret['2008-01-01/2020-01-01'], bench.ret['2008-01-01/2020-01-01'],SPY.ret['2008-01-01/2020-01-01']),
                                   c("Strategy","Benchmark","SPY"))
cal_annual_ret
#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value['2008-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) ##border is set to NA, otherwise with daily data, there is to much black border, the chart appears to be black
```

## Data from 2015-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret['2015-01-01/2020-01-01'], bench.ret['2015-01-01/2020-01-01'],SPY.ret['2015-01-01/2020-01-01']))

```

```{r echo=FALSE}
ret<-cbind(portf.ret['2015-01-01/2020-01-01'], bench.ret['2015-01-01/2020-01-01'],SPY.ret['2015-01-01/2020-01-01'])
colnames(ret)<-c("TDM","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret['2015-01-01/2020-07-14'], bench.ret['2015-01-01/2020-07-14'],SPY.ret['2015-01-01/2020-07-14']),
                                   c("Strategy","Benchmark","SPY"))
cal_annual_ret

#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value['2015-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) ##border is set to NA, otherwise with daily data, there is to much black border, the chart appears to be black
```

## Data from 2017-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret['2017-01-01/2020-01-01'], bench.ret['2017-01-01/2020-01-01'],SPY.ret['2017-01-01/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret['2017-01-01/2020-01-01'], bench.ret['2017-01-01/2020-01-01'],SPY.ret['2017-01-01/2020-01-01'])
colnames(ret)<-c("TDM","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret['2017-01-01/2020-07-14'], bench.ret['2017-01-01/2020-07-14'],SPY.ret['2017-01-01/2020-07-14']),
                                   c("Strategy","Benchmark","SPY"))
cal_annual_ret

#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value['2017-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) ##border is set to NA, otherwise with daily data, there is to much black border, the chart appears to be black
```

## Data from 2019-01-01 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret['2019-01-01/2020-01-01'], bench.ret['2019-01-01/2020-01-01'],SPY.ret['2019-01-01/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret['2019-01-01/2020-01-01'], bench.ret['2019-01-01/2020-01-01'],SPY.ret['2019-01-01/2020-01-01'])
colnames(ret)<-c("TDM","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret['2019-01-01/2020-07-14'], bench.ret['2019-01-01/2020-07-14'],SPY.ret['2019-01-01/2020-07-14']),
                                   c("Strategy","Benchmark","SPY"))
cal_annual_ret

#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value['2019-01-01/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) ##border is set to NA, otherwise with daily data, there is to much black border, the chart appears to be black
```

## Data from 2019-06-30 to 2020-01-01
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret['2019-06-30/2020-01-01'], bench.ret['2019-06-30/2020-01-01'],SPY.ret['2019-06-30/2020-01-01']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret['2019-06-30/2020-01-01'], bench.ret['2019-06-30/2020-01-01'],SPY.ret['2019-06-30/2020-01-01'])
colnames(ret)<-c("TDM","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret['2019-06-30/2020-07-14'], bench.ret['2019-06-30/2020-07-14'],SPY.ret['2019-06-30/2020-07-14']),
                                   c("Strategy","Benchmark","SPY"))
cal_annual_ret

#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value['2019-06-30/2020-01-01'], date.format="%y/%m", colorset=rainbow12equal, border=NA) ##border is set to NA, otherwise with daily data, there is to much black border, the chart appears to be black
```

## Year to Date
### Performance Summary
```{r echo=FALSE}
tab.perf(cbind(portf.ret['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14']))
```

```{r echo=FALSE}
ret<-cbind(portf.ret['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14'])
colnames(ret)<-c("TDM","bench","SPY")
charts.PerformanceSummary(ret, date.format="%Y%m")
```

### Portfolio Calendar Year Returns
```{r echo=FALSE}

cal_annual_ret<-gen_cal_annual_ret(cbind(portf.ret['2020-01-01/2020-07-14'], bench.ret['2020-01-01/2020-07-14'],SPY.ret['2020-01-01/2020-07-14']),
                                   c("Strategy","Benchmark","SPY"))
cal_annual_ret

#grid.newpage()
#grid.table(cal_annual_ret)
```

### Portfolio Weights over time
```{r echo=FALSE}
chart.StackedBar(portf$BOP.Value['2020-01-01/2020-07-14'], date.format="%y/%m", colorset=rainbow12equal, border=NA) ##border is set to NA, otherwise with daily data, there is to much black border, the chart appears to be black
```